Learning Auditory Similarities Between Instrumental Playing Techniques

### 2019-10-02 paper/paper.tex
Add discussion of model in introduction

In this paper, we propose a machine listening model which computes the dissimilarity in timbre between any two audio samples.

\ml{decrire les contributions signal ici}

>>>>

In this paper, we propose a machine listening model which computes the dissimilarity in timbre between any two audio samples.
It is composed of two stages, one fixed and one learned, the former providing a baseline model for audio perception, with the latter specifically adapting the representation for estimation of timbre similarity.
The fixed stage is constructed using the joint time--frequency scattering transform introduced by And\'en et al. \cite{anden2015joint,anden2019joint}.
This representation extracts the time--frequency structure of the audio signal in a manner invariant to small time-shifts and stable to time-warping deformations.
As such, it provides a general description of the audio signal that is not necessarily tailored to measuring timbre similarity.
The second stage consists of a learned linear transform that, applied to the scattering representation, induces a metric that more closely aligns with timbre similarity judgments extracted from human listeners.
We see that, numerically, this learned metric almost exactly reproduces the human similarity judgments.
Moreover, we perform an ablation study of the model showing that degrading any element of it (replacing the scattering transform by simpler spectral descriptors, for example) significantly reduces the accuracy of the fit.
